Reanalysis Step 5: Outcome Analysis with Three-Way Interaction

### 2025-09-04 reanalysis-5-outcome_analysis-interaction.qmd
bug

@@

  # Save to cache with full structure
  cached_data <- list(
    models = models,
    model_progress = model_progress,
    formula_used = interaction_formula,
    n_imputations = n_imputations,
    timestamp = Sys.time()
  )
  saveRDS(cached_data, models_cache_file)
  cache_location <- models_cache_file
  log_message("Models fitted and saved to cache: ", cache_location)
}

>>>>

  # Extract or initialize model_summaries
  if ("model_summaries" %in% names(cached_data)) {
    model_summaries <- cached_data$model_summaries
  } else {
    # Rebuild model_summaries from models if not in cache
    model_summaries <- list()
    for (i in 1:length(models)) {
      model_summaries[[i]] <- summary(models[[i]])$coefficients
    }
  }

@@

  # Save to cache with full structure
  cached_data <- list(
    models = models,
    model_summaries = model_summaries,
    model_progress = model_progress,
    formula_used = interaction_formula,
    n_imputations = n_imputations,
    timestamp = Sys.time()
  )
  saveRDS(cached_data, models_cache_file)
  cache_location <- models_cache_file
  log_message("Models fitted and saved to cache: ", cache_location)
}
